Stellar Radiation is Critical for Regulating Star Formation and Driving Outflows in Low Mass Dwarf Galaxies

### 2018-07-31 ms.tex
including Smith references in introduction. couple typos. removing repeated bibtex entries

\author{Andrew Emerick}
\affil{Columbia University}
\affil{Department of Astrophysics, American Museum of Natural History, New York, NY 10024}

\author{Greg L. Bryan}
\affiliation{Columbia University}
\affiliation{Flatiron Institute}

\author{Mordecai-Mark Mac Low}
%mm [I've been asked to use my Columbia affiliation when working with CU students]
\affil{Department of Astrophysics, American Museum of Natural History, New York, NY 10024}
\affiliation{Columbia University}

@@

\section{Introduction} \label{sec:intro}
Historically, simulations of galaxy formation have suffered from the ``overcooling'' problem, whereby the action of self-gravity and radiative cooling alone produces galaxies with far too many stars. This problem has been addressed by employing various models of strong stellar feedback physics which are capable of generating self-regulating star formation in galaxies (see \cite{SomervilleDave2015} and \cite{NaabOstriker2017} for recent reviews). \textbf{Energy injection from supernovae (SNe) has historically been used as the sole form of feedback. However, this is generally done heuristically as many simulations lack the ability to resolve the Sedov phase of individual SNe. But even with this strong feedback, recent work has argued for the need for pre-SN feedback, from stellar winds and/or stellar radiation \citep[e.g.][]{Hu2016,Hopkins2018}, though this is typically modeled simply as additional energy injection around newly formed stars. The need for additional feedback is confirmed by simulations that are capable of fully resolving individual SN \citep[e.g.][]{Peters2017,Hu2018}. However, modeling these processes in detail is challenging, and their competing effects on galactic evolution are poorly constrained.}

@@

In this work we use a detailed model for stellar feedback presented in \cite{Emerick2018} (hereafter Paper I) to study the role of radiation feedback in dwarf galaxy evolution. For the first time in a galaxy-scale simulation, we resolve individual HII using an adaptive ray tracing radiative transfer method to follow the ionizing radiation from particles that represent individual stars. We focus on addressing two questions: 1) what role does radiation feedback play in regulating star formation, and 2) are the long-range effects of radiation feedback important, or is the local destruction of dense gas the dominant effect.

>>>>

\author{Andrew Emerick}
\affil{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
\affil{Department of Astrophysics, American Museum of Natural History, New York, NY 10024}

\author{Greg L. Bryan}
\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY, 10003, U.S.A}

\author{Mordecai-Mark Mac Low}
%mm [I've been asked to use my Columbia affiliation when working with CU students]
\affil{Department of Astrophysics, American Museum of Natural History, New York, NY 10024}
\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}

@@

\section{Introduction} \label{sec:intro}
Historically, simulations of galaxy formation have suffered from the ``overcooling'' problem, whereby the action of self-gravity and radiative cooling alone produces galaxies with far too many stars. This problem has been addressed by employing various models of strong stellar feedback physics which are capable of generating self-regulating star formation in galaxies (see \cite{SomervilleDave2015} and \cite{NaabOstriker2017} for recent reviews). \textbf{Energy injection from supernovae (SNe) has historically been used as the sole form of feedback. However, this is generally done heuristically as many simulations lack the ability to resolve the Sedov phase of individual SNe. But even with this strong feedback, recent work has argued for the need for pre-SN feedback, from stellar winds and/or stellar radiation \citep[e.g.][]{Hu2016,Hopkins2018}, though this is typically modeled simply as additional energy injection around newly formed stars. The need for additional feedback is confirmed by simulations that are capable of fully resolving individual SN \citep[e.g.][]{Peters2017,Smith2018a,Smith2018b,Hu2018}. However, modeling these processes in detail is challenging, and their competing effects on galactic evolution are poorly constrained.}

@@

In this work we use a detailed model for stellar feedback presented in \cite{Emerick2018} (hereafter Paper I) to study the role of radiation feedback in dwarf galaxy evolution. For the first time in a galaxy-scale simulation, we resolve individual HII rgeions using an adaptive ray tracing radiative transfer method to follow the ionizing radiation from particles that represent individual stars. We focus on addressing two questions: 1) what role does radiation feedback play in regulating star formation, and 2) are the long-range effects of radiation feedback important, or is the local destruction of dense gas the dominant effect.
